\LaTeX\ Author Guidelines for ICCV Proceedings

### 2019-05-13 chapters/5_experiments_compare_rules.tex

\textbf{Training details} \UPDATE{We pre-aligned the training and test data with an elastic alignment method \cite{saalfeld2012elastic}. We further simulated low contrast sections... and missing sections by setting their intensity value to zero... We used 3D U-Net architecture \cite{ronneberger2015u,cciccek20163d} trained with L1 loss (Adam optimizer with learning rate...).}

>>>>

\textbf{Training details}
To alleviate difficulties in segmentation, we use a version of the data that was elastically aligned by the challenge organizers with the method \cite{saalfeld2012elastic}.
We train a 3D U-Net \cite{ronneberger2015u, cciccek20163d} using the same architecture as \cite{funke2018large} and predict long-and-short range affinities 
as described in \cite{lee2017superhuman}. In addition to the standard data augmentation techniques of random rotations, random flips and elastic deformations, we simulate data artifacts.
In more detail, we randomly zero-out slices, decrease the contrast of slices, simulate tears, introduce alignment jitter and paste artifacts extracted from the training data. Both \cite{funke2018large} and \cite{lee2017superhuman} have shown
that these kinds of augmentations can help to alleviate issues caused by EM-imaging artifacts.
We use L2 loss and Adam optimizer to train the network.
%\UPDATE{We pre-aligned the training and test data with an elastic alignment method \cite{saalfeld2012elastic}. We further simulated low contrast sections... and missing sections by setting their intensity value to zero... We used 3D U-Net architecture \cite{ronneberger2015u,cciccek20163d} trained with L1 loss (Adam optimizer with learning rate...).}
